An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-02-18 paper.tex
Simplified stride width calc and shorted x tick labels on boxplot.

For more insight into the difference in the unperturbed and perturbed data,
Figure~\ref{fig:gait-cycle-stats-comparison} compares the distribution of a few
gait cycle statistics. One can see that the perturbed strides have a much
larger variation in frequency and length.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-boxplot-comparison.pdf}
  \cprotect\caption{Box plots of the average belt speed, stride frequency, and
    stride length which compare unperturbed (red) and perturbed (blue) gait
    cycles. The median is given with the box bounding the first and third
    quartiles and the whiskers bound the range of the data. Produced by
    \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:gait-cycle-stats-comparison}
\end{figure}

>>>>

For more insight into the difference in the unperturbed and perturbed data,
Figure~\ref{fig:gait-cycle-stats-comparison} compares the distribution of a few
gait cycle statistics. One can see that the perturbed strides have a much
larger variation in frequency and length and even larger variation in stride
width.
%
\begin{figure}
  \centering
  \includegraphics{figures/unperturbed-perturbed-boxplot-comparison.pdf}
  % NOTE : Make sure to update these values (120, 519) if anything in the
  % script changes.
  \cprotect\caption{Box plots of the average belt speed, stride frequency,
    stride length, and stride width which compare 120 unperturbed (U: red) and
    519 perturbed (P: blue) gait cycles. The median is given with the box
    bounding the first and third quartiles and the whiskers bound the range of
    the data. Produced by \verb|src/unperturbed_perturbed_comparison.py|.}
  \label{fig:gait-cycle-stats-comparison}
\end{figure}
